\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-05-03 ase20/conclusion.tex
[ASE] Fill all numbers

\section{Conclusion}\label{sec:conclude}
Annual updates of ECMAScript make it difficult to build program
analysis or formal verification of JavaScript due to the required human efforts
in modeling a moving target.  In this paper, we proposed \( \tool \), a tool
that \textit{automatically} extracts the syntax and semantics as a parser and
an AST-IR translator from ECMAScript written in English.
The tool automatically extracts all the syntax and \inred{XX.XX\%} of the
semantics for the most recent four versions of ECMAScript (ES7 to ES10).
We evaluated the correctness of the tool by testing the extracted
semantics from ES10 with Test262, the official conformance suite.
Using \inred{X,XXX} failed tests, we found nine specification errors,
four of which are newly discovered, confirmed by TC39, and planned to
be integrated in ES11.  After fixing the errors, the extracted
semantics passed all \inred{XX,XXX} applicable tests in Test262.
We also showed that \( \tool \) is forward compatible by applying it to nine
proposals to be included in ES11, which let us find three errors in the
BigInt proposal.  We believe that \( \tool \) can dramatically reduce
human efforts in building various JavaScript tools correctly.

>>>>

\section{Conclusion}\label{sec:conclude}
Annual updates of ECMAScript make it difficult to build program
analysis or formal verification of JavaScript due to the required human efforts
in modeling a moving target.  In this paper, we proposed \( \tool \), a tool
that \textit{automatically} extracts the syntax and semantics as a parser and
an AST-IR translator from ECMAScript written in English.
The tool automatically extracts all the syntax and 95.03\% of the
semantics for the most recent four versions of ECMAScript (ES7 to ES10).
We evaluated the correctness of the tool by testing the extracted
semantics from ES10 with Test262, the official conformance suite.
Using 1,709 failed tests, we found nine specification errors,
four of which are newly discovered, confirmed by TC39, and planned to
be integrated in ES11.  After fixing the errors, the extracted
semantics passed all 18,064 applicable tests in Test262.
We also showed that \( \tool \) is forward compatible by applying it to nine
proposals to be included in ES11, which let us find three errors in the
BigInt proposal.  We believe that \( \tool \) can dramatically reduce
human efforts in building various JavaScript tools correctly.

### 2020-05-03 ase20/intro.tex
[ASE] Removed bigint-3 / Updated Table 5
[ASE] Fill all numbers

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    95.03\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between the specification written in a
    natural language and tests.}
    To evaluate the correctness of \( \tool \), we checked the extracted
    semantics with the official test conformance suite, Test262~\cite{test262}.
    By manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), we defined the \textit{first IR-based formal
    semantics of modern JavaScript}. It failed for \inred{XXXX} tests because of
    specification errors in ES10. Using the tests, we found eight specification errors,
    three of which had not been reported before. They were all confirmed by
    TC39 and will be fixed in the next release.  After fixing them, the formal
    semantics passed all 18,064 applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    nine proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found four specifications errors in BigInt
    proposal by executing the corresponding tests in Test262.  After fixing
    them, the extracted semantics passed all \inred{XXX} tests.
\end{itemize}

>>>>

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    95.03\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between the specification written in a
    natural language and tests.}
    To evaluate the correctness of \( \tool \), we checked the extracted
    semantics with the official test conformance suite, Test262~\cite{test262}.
    By manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), we defined the \textit{first IR-based formal
    semantics of modern JavaScript}. It failed for 1,709 tests because of
    specification errors in ES10. Using the tests, we found eight specification errors,
    three of which had not been reported before. They were all confirmed by
    TC39 and will be fixed in the next release.  After fixing them, the formal
    semantics passed all 18,064 applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    nine proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled 560
    out of 595 algorithm steps for all the proposals.  After completion
    of the missing parts, we found three specifications errors in BigInt
    proposal by executing the corresponding tests in Test262.  After fixing
    them, the extracted semantics passed all applicable ES10 tests and 303 new
    applicable tests.
\end{itemize}
